How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-20 docs/PhysicsPaper/StokesErosion.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% COMMANDS
% Basic editing
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\tocite}{ {\color{blue}(to cite)} }
\newcommand{\nick}[1]{ {\color{red} #1} }
\newcommand{\edit}[1]{{\color{red} #1}}

@@

Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows~\cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows~\cite{chiu2020viscous, szymczak2009wormhole, jager2017channelization, grodzki2019reactive, bizmark2020multiscale, derr2020flow, zareei2022temporal}. The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials. Porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others. Typical materials are more permeable to flow in the \edit{horizontal} direction than \edit{the vertical} by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}. Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}. Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work. Here, we use numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% COMMANDS
% Basic editing
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
\newcommand{\tocite}{ {\color{blue}(to cite)} }

\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\black}[1]{#1}
\newcommand{\edit}[1]{\red{#1}}

@@

Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water~\cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows~\cite{berhanu2012shape, bertagni2021hydrodynamic, weady2022anomalous}, and down to granular and porous networks slowly disintegrating in groundwater flows~\cite{chiu2020viscous, szymczak2009wormhole, jager2017channelization, grodzki2019reactive, bizmark2020multiscale, derr2020flow, zareei2022temporal}. The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting large-scale features as well as small-scale ones, such as the microstructure of porous materials. Porous media encountered in nature typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others. 
\edit{Most commonly, this anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plane of deposition~\cite{bear1988dynamics}. This idea is supported by the observation that natural materials are typically more permeable in the horizontal direction than the vertical by a factor of 5--20~\cite{bear1988dynamics, anderson2015applied}.}
Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work. Here, we use numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.
